Late Pleistocene stone artefact technology at Mau A, Yen Bai, Norther Vietnam

### 2022-02-25 analysis/paper/paper.Rmd
suppress unwanted messages that appear in the docx, minor formatting edits

lands <- readland.tps(
  here::here("analysis/data/derived_data/landmarks.tps"),
  specID = "ID")

@@

sup.geo <- gpagen(lands_no_outliers,  ProcD=F, Proj = T)

@@

```{r cortex-biplot}
# Note, trying to fix NA by removing all rows which lack dorsal cortex values. Issue with the initial set of data with NA values being passed through PCA. In the process of fixing

# Adding extra groups needed for biplots, as well as removing the outliers brought up earlier

@@

<!-- QH: Later on, the language "the visualization above" will be changed to "Figure X." -->
<!-- QH: Also, on a secondary note, I had to copy the data file into a different location. That means that there are redundant data files that will need to be cleaned up later -->

<!--“biplot above” replace this figure \@ref(fig:code-block-name)  code-block-name is like this ```{r code-block-name} be sure to give them descriptive, simple names -->

@@

```{r excavation-unit-biplot}
# Excavation unit PCA
# ggplot2-based plot of the PCA results using a factoextra function
fviz_pca_ind(pca.geo,
             geom.ind = "point", # show points without labels
            #  line below sets the grouping column for colouring the points
             habillage = as.factor(ma_flakes_tr_with_groups$Unit),
             palette = viridis::cividis(13), # color palette, adjust to preferences
             addEllipses = T, #adds ellipses or convex hulls
             ellipse.type = "convex", #convex hulls
             mean.point = F, #don’t show average point
             legend.title = "Excavation\nunit",
             title = "Change over time in flake shape") +  #adjust accordingly)
             coord_fixed(ratio = 1)  + #adjustable for variation-weighted plots
             theme(panel.background = element_rect(fill='white',
                                        colour = "white"),
              plot.background = element_rect(fill='white',
                                       colour = "white")) +
    theme(plot.title = element_blank())
```
<!-- This portion is lifted largely from the ISKM presentation. Might well reword it later, but it will do for now -->

@@

```{r mass-biplot}

# Mass PCA
# ggplot2-based plot of the PCA results using a factoextra function
fviz_pca_ind(pca.geo,
             geom.ind = "point", # show points without labels
            #  line below sets the grouping column for colouring the points
             habillage = ma_flakes_tr_with_groups$mass_group,
             palette = viridis::viridis(6), #color palette, adjust to preferences
             addEllipses = T, #adds ellipses or convex hulls
             ellipse.type = "convex", #convex hulls
             mean.point = F, #don’t show average point
             legend.title = "Mass\ncluster",  #adjust accordingly
            title = "Flake mass and flake shape") + 
             coord_fixed(ratio = 1) + #adjustable for variation-weighted plots
             theme(panel.background = element_rect(fill='white',
                                        colour = "white"),
              plot.background = element_rect(fill='white',
                                       colour = "white")) +
    theme(plot.title = element_blank())

>>>>

lands <- readland.tps(
  here::here("analysis/data/derived_data/landmarks.tps"),
  specID = "ID",
  warnmsg = FALSE)

@@

sup.geo <- gpagen(lands_no_outliers,  
                  ProcD=F, 
                  Proj = T,
                  print.progress = FALSE)

@@

```{r cortex-biplot, fig.cap="PCA biplot for flake shape and dorsal cortex class."}

@@

@@

```{r excavation-unit-biplot, fig.cap="PCA biplot for flake shape and excavation unit."}
# Excavation unit PCA
# ggplot2-based plot of the PCA results using a factoextra function
fviz_pca_ind(pca.geo,
             geom.ind = "point", # show points without labels
            #  line below sets the grouping column for colouring the points
             habillage = as.factor(ma_flakes_tr_with_groups$Unit),
             palette = viridis::cividis(13), # color palette, adjust to preferences
             addEllipses = T, #adds ellipses or convex hulls
             ellipse.type = "convex", #convex hulls
             mean.point = F, #don’t show average point
             legend.title = "Excavation\nunit",
             title = "Change over time in flake shape") +  #adjust accordingly)
             coord_fixed(ratio = 1)  + #adjustable for variation-weighted plots
             theme(panel.background = element_rect(fill='white',
                                        colour = "white"),
              plot.background = element_rect(fill='white',
                                       colour = "white")) +
    theme(plot.title = element_blank())
```

<!-- This portion is lifted largely from the ISKM presentation. Might well reword it later, but it will do for now -->

@@

```{r mass-biplot, fig.cap="PCA biplot for flake shape and mass cluster groups"}

# Mass PCA
# ggplot2-based plot of the PCA results using a factoextra function
fviz_pca_ind(pca.geo,
             geom.ind = "point", # show points without labels
            #  line below sets the grouping column for colouring the points
             habillage = ma_flakes_tr_with_groups$mass_group,
             palette = viridis::viridis(6), #color palette, adjust to preferences
             addEllipses = T, #adds ellipses or convex hulls
             ellipse.type = "convex", #convex hulls
             mean.point = F, #don’t show average point
             legend.title = "Mass\ncluster",  #adjust accordingly
            title = "Flake mass and flake shape") + 
             coord_fixed(ratio = 1) + #adjustable for variation-weighted plots
             theme(panel.background = element_rect(fill='white',
                                        colour = "white"),
              plot.background = element_rect(fill='white',
                                       colour = "white")) +
    theme(plot.title = element_blank())
```
